\textbf{Are regime changes always bad economics? Evidence from daily financial data}

### 2019-04-25 doc/paper.tex
Update sensitivity results so trading day 0 is an anchor day

We explore these concerns in a number of ways. First, we reestimate mean CARs on a set of time-shifted placebo dates. Means are computed across all events within a given type of regime change. We shift event dates surrounding the actual event date backwards and forwards in increments of five days (-20, 15, 10, 5, 0, 5, 10, 15, and 20 days). In addition, we extend the forward shifted event date out to one year (110, 195, 285, and 365 days) to capture dates that are likely to be completely unaffected by the regime change.

>>>>

We explore these concerns in two ways. First, we reestimate mean CARs on a set of time-shifted placebo dates, with means computed across all events within a given type of regime change. We shift event dates surrounding the actual event date backwards and forwards in increments of five days (-20, 15, 10, 5, 0, 5, 10, 15, and 20 days). In addition, we extend the forward shifted event dates to one year (110, 195, 285, and 365 days) to capture dates that are likely to be completely unaffected by the regime change.
